---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# pronto                                                                    

pronto is a simple R package for interacting with data from from Seattle's [Pronto](http://www.prontocycleshare.com) cycle sharing system.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.


# Installation                                                                  

`pronto` is not on [CRAN](http://cran.r-project.org/), but you can use      
[devtools](http://cran.r-project.org/web/packages/devtools/index.html) to       
install the latest and greatest version. To do so:                              

```{r, eval=FALSE}
if(!require("devtools")) install.packages("devtools")                       
devtools::install_github("briandconnelly/pronto")
```

# Examples

## Get current station data

```{r Example get}
library(pronto)

stations <- pronto_stations()
```

## Plotting system information

Let's make a map of current bike availability across the city using [ggmap](https://github.com/dkahle/ggmap).

*coming soon!*


# Disclaimer

Neither this package nor its contributer(s) are affiliated with Pronto.
